Papers

### 2025-07-29 index.qmd
fix author orderings

<font color="#d08770">[June 13 2024].</font> **Paper accepted**. Calalo JA, Ngo T, Sullivan S, Roth A, Lokesh R, Buggeln JH, Strand K, Marchhart V, Carter MJ, Kurtzer I, & Cashaback JGA. (Accepted). Online movements reflect ongoing deliberation. *Journal of Neuroscience*. [https://doi.org/10.1523/JNEUROSCI.1913-24.2025](https://doi.org/10.1523/JNEUROSCI.1913-24.2025){target="_blank"}

<font color="#d08770">[May 14 2024].</font> **Paper accepted**. Sullivan SR, Lokesh R, Peters CS, Calalo J, Roth AR, Buggeln JH, Ngo TT, Carter MJ, & Cashaback JGA. (In Press). Indecision under time pressure arises from suboptimal switching behaviour. *Journal of Neurophysiology*. [https://doi.org/10.1152/jn.00563.2024](https://doi.org/10.1152/jn.00563.2024){target="_blank"}

>>>>

<font color="#d08770">[June 13 2024].</font> **Paper accepted**. Calalo JA, Ngo T, Sullivan S, Strand K, Buggeln JH, Lokesh R, Roth A, Carter MJ, Kurtzer IL, & Cashaback JGA. (Accepted). Online movements reflect ongoing deliberation. *Journal of Neuroscience*. [https://doi.org/10.1523/JNEUROSCI.1913-24.2025](https://doi.org/10.1523/JNEUROSCI.1913-24.2025){target="_blank"}

<font color="#d08770">[May 14 2024].</font> **Paper accepted**. Sullivan SR, Lokesh R, Calalo J, Ngo TT, Buggeln JH, Roth AR, Peters CS, Kurtzer IL, Carter MJ, & Cashaback JGA. (In Press). Indecision under time pressure arises from suboptimal switching behaviour. *Journal of Neurophysiology*. [https://doi.org/10.1152/jn.00563.2024](https://doi.org/10.1152/jn.00563.2024){target="_blank"}

### 2025-07-29 papers.qmd
add doi for jneurosci paper
fix author orderings

- Calalo JA, Ngo T, Sullivan S, Roth A, Lokesh R, Buggeln JH, Strand K, Marchhart V, Carter MJ, Kurtzer I, & Cashaback JGA. (Accepted). Online movements reflect ongoing deliberation. *Journal of Neuroscience*.

@@

- Sullivan SR., Lokesh R., Peters CS., Calalo J., Roth AR., Buggeln JH., Ngo TT., Carter MJ., & Cashaback JGA. (2025). Indecision under time pressure arises from suboptimal switching behaviour. *Journal of Neurophysiology*. ---
[{{< ai doi >}}](https://doi.org/10.1152/jn.00563.2024){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_sullivan-etal_indecision-under-time-pressure-arises-from-suboptimal-switching-behavior.pdf){target="_blank" style="color: inherit;"}

>>>>

- Calalo JA., Ngo T., Sullivan S., Strand K., Buggeln JH., Lokesh R., Roth A., Carter MJ., Kurtzer IL., & Cashaback JGA.. (Accepted). Online movements reflect ongoing deliberation. *Journal of Neuroscience*. ---
[{{< ai doi >}}](https://doi.org/10.1523/JNEUROSCI.1913-24.2025){target="_blank" style="color: inherit;"}

@@

- Sullivan SR., Lokesh R., Calalo J., Ngo TT., Buggeln JH., Roth AR., Peters CS., Kurtzer IL., Carter MJ., & Cashaback JGA. (2025). Indecision under time pressure arises from suboptimal switching behaviour. *Journal of Neurophysiology*. ---
[{{< ai doi >}}](https://doi.org/10.1152/jn.00563.2024){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_sullivan-etal_indecision-under-time-pressure-arises-from-suboptimal-switching-behavior.pdf){target="_blank" style="color: inherit;"}
